An Integral-field Spectroscopic Study of Low-power Radio Galaxies

### 2020-01-01 paper.tex
Work on plots in paper
Corrected issue with NI-NII 'dec', and minor alterations to maps.

 On branch master
 Changes to be committed:
	modified:   EqW_fit.png
	modified:   paper.tex
	modified:   produce_kine_plot.py
	modified:   ratio_fit.png

\citet{Bender1993} observed a tight relationship between the \added{central} \removed{global}
Mg$_2$ absorption line strength (a variant of the Mg~$b$ line
strength) and the logarithm of the central stellar velocity
dispersion, $\sigma_0$, in elliptical galaxies. \removed{They also noticed that
the residuals from the best-fitting linear relation appeared to be
intrinsic, with a near Gaussian distribution about the median value
\textbf{(Was that median value $\approx0$? If so, state explicitly. If
  not, then the fit was either bad or there is something we do not
  understand.)} and no correlation with any other galaxy property.}

@@

\added{\citet{McDermid2006}} \removed{\citet{Kuntschner2010}} showed that 
KDCs can be separated into two classes: either small with various stellar 
ages or typically larger but containing a homogeneously old stellar 
population. {\bf (I thought the first to point this out was 
McDermid et al.\ (2006; see e.g.\ their Fig.~16), which should at 
least also be quoted here. Check and possibly correct.)} 
\added{Using the method of \ctiet{McDermid2006},} the size 
\added{and age} of the KDC is defined as the radius
where the superposition of the two kinematic components (the KDC and
the host galaxy) results in a local minimum in the mean velocity \added{and} the
age of the most-likely SSP model for the spatially integrated spectrum
within a central \added{, circular} aperture with a \added{radius} of 
$1\arcsec$ {\bf (Again, square or circular, radius or diameter? Clarify.)} 
\removed{is taken as the KDC's age.} \added{, respectively.} 
{\bf (Are these two definitions (of the KDCs' sizes and ages) 
those of \citealt{Kuntschner2010} or yours or both? Clarify.)}

@@

\removed{\textbf{IC~1459} has ionised gas counter-rotating with respect to the
stellar KDC, but it is also misaligned with respect to the outer stars
of the host galaxy (i.e.\ the stars beyond the KDC), that are
non-rotating (see Fig.~\ref{fig:ic1459}). The ionised gas thus appears
to have a third, independent, axis of rotation. {\bf (I do not
  understand why you state/claim that here. From the map shown, it
  seems pretty clear to me that the stars in the outer parts of the
  galaxy {\em are} rotating (i.e.\ the top-left is red and the
  bottom-right is blue), and that they are rotating in a manner
  consistent with the ionised gas, just as \citet{Franx1988}
  claimed. Convince me otherwise of change your statement!)} This is
contrary to \citet{Franx1988} who claims that the rotation of the gas
is aligned with that of the stars outside of the KDC. As the stellar
disc did not survive the merger event that created the KDC, {\bf (How
  do you know there was a stellar disc to start with? Clarify or
  rephrase.)} it is unlikely that the gas in the progenitor of IC~1459
survived. However, the lost gas may have remained bound and been
re-accreted, so that the gas observed today preserves a fossil record
of the galaxy's original disc. Alternatively, the ISM may have yet
another external origin.}

@@

Generally, if we assume that the different ionisation states of a
given atomic species occur in the same spatial location, then
shielding by dust is not important or at worst its effect on the
emission-line ratios is linear. {\bf (Why is the effect only linear?
  Justify.)} Given that the different states are then produced under
the same conditions, it is natural to expect a simple relationship
between their emission line fluxes, similar to that of the Balmer
decrement between H$\alpha$ and H$\beta$. We exploit such
relationships here, to transform the classification boundaries of
commonly-used diagnostic plots that utilise emission lines outside of
the VIMOS spectral range, to diagnostics that can be measured with our
VIMOS data. In particular, we transform the classic BPT
[\ion{N}{ii}]/H$\alpha$ versus [\ion{O}{iii}]/H$\beta$ diagram to
[\ion{N}{i}]/H$\beta$ versus [\ion{O}{iii}]/H$\beta$ (hereafter the
SAURON diagnostic plot) following \citet{Sarzi2010}.

@@

The two transformations that we use are from the
[\ion{N}{ii}]/H$\alpha$ to the [\ion{N}{i}]/H$\beta$ line ratio and
from the H$\alpha$ to the H$\beta$ equivalent width (EW). In both
cases, we fit a linear relationship using the least-trimmed squares
routine
\textsc{lts\_linefit}\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/\#lts}
of \citet{Cappellari2013}, because of its robust handling of the
uncertainties along both axes. The linear relationships are shown in
Figs.~\ref{fig:ratio_relation} and \ref{fig:EqW_relation}, where we
respectively find
\begin{equation}
  \frac{[\text{\ion{N}{ii}}]}{H\alpha}=(0.38\pm0.02)\,\frac{[\text{\ion{N}{i}}]}{H\beta}+(1.80\pm0.02)
\end{equation}
and	
\begin{equation}
  \mathrm{EW}(H\alpha)=(2.92\pm0.03)\,\mathrm{EW}(H\beta)-(0.16\pm0.02)~.
  \label{eq:EqW_dec}
\end{equation}
As [\ion{N}{ii}]/H$\alpha<1.80$ is occasionally observed and would
result in an unphysical negative [\ion{N}{i}]/H$\beta$ line ratio if
used blindly, we instead use the following transformation in practice:
\begin{equation}
  \frac{[\text{\ion{N}{i}}]}{H\beta}= 
  \begin{cases}
    (0.38\pm0.02)\,\frac{[\text{\ion{N}{iI}}]}{H\alpha}+(1.80\pm0.02), & \text{if}~\frac{[\text{\ion{N}{ii}}]}{H\alpha}<2 \\
    (0.38\pm0.02)\,\frac{[\text{\ion{N}{ii}}]}{H\alpha}, & \text{otherwise.}
  \end{cases}
  \label{eq:N_dec}
\end{equation}

{\bf (There is something very wrong about this last set of
  equations. First, since you presumably want to infer
  $\frac{[\text{\ion{N}{i}}]}{H\beta}$ from
  $\frac{[\text{\ion{N}{iI}}]}{H\alpha}$ and EW(H$\beta$) from
  EW(H$\alpha$), why not report (and presumably fit for in the first
  place) the inverse of the Eqs.~A1 and A2. Second, you have switched
  $\frac{[\text{\ion{N}{i}}]}{H\beta}$ and
  $\frac{[\text{\ion{N}{iI}}]}{H\alpha}$ in Eq.~A3, which is clearly
  wrong. You should probably switch them back. In addition, the
  conditions stated in Eq.~A3 make no sense. Presumably, one should
  follow the relation until $\frac{[\text{\ion{N}{i}}]}{H\beta}=0$,
  and then leave it at $0$. In any case, these equations need to be
  fixed.)}

>>>>

\citet{Bender1993} observed a tight relationship between the \added{central} \removed{global}
Mg$_2$ absorption line strength (a variant of the Mg~$b$ line
strength) and the logarithm of the central stellar velocity
dispersion, $\sigma_0$, in elliptical galaxies. \removed{They also noticed that
the residuals from the best-fitting linear relation appeared to be
intrinsic, with a near Gaussian distribution about the median value}
{\bf (Was that median value $\approx0$? If so, state explicitly. If
  not, then the fit was either bad or there is something we do not
  understand.)} \removed{and no correlation with any other galaxy property.}

@@

\added{\citet{McDermid2006}} \removed{\citet{Kuntschner2010}} showed that 
KDCs can be separated into two classes: either small with various stellar 
ages or typically larger but containing a homogeneously old stellar 
population. {\bf (I thought the first to point this out was 
McDermid et al.\ (2006; see e.g.\ their Fig.~16), which should at 
least also be quoted here. Check and possibly correct.)} 
\added{Using the method of \citet{McDermid2006},} the size 
\added{and age} of the KDC is defined as the radius
where the superposition of the two kinematic components (the KDC and
the host galaxy) results in a local minimum in the mean velocity \added{and} the
age of the most-likely SSP model for the spatially integrated spectrum
within a central \added{, circular} aperture with a \added{radius} of 
$1\arcsec$ {\bf (Again, square or circular, radius or diameter? Clarify.)} 
\removed{is taken as the KDC's age.} \added{, respectively.} 
{\bf (Are these two definitions (of the KDCs' sizes and ages) 
those of \citealt{Kuntschner2010} or yours or both? Clarify.)}

@@

\removed{\textbf{IC~1459} has ionised gas counter-rotating with respect to the
stellar KDC, but it is also misaligned with respect to the outer stars
of the host galaxy (i.e.\ the stars beyond the KDC), that are
non-rotating (see Fig.~\ref{fig:ic1459}). The ionised gas thus appears
to have a third, independent, axis of rotation.} {\bf (I do not
  understand why you state/claim that here. From the map shown, it
  seems pretty clear to me that the stars in the outer parts of the
  galaxy {\em are} rotating (i.e.\ the top-left is red and the
  bottom-right is blue), and that they are rotating in a manner
  consistent with the ionised gas, just as \citet{Franx1988}
  claimed. Convince me otherwise of change your statement!)} \removed{This is
contrary to \citet{Franx1988} who claims that the rotation of the gas
is aligned with that of the stars outside of the KDC. As the stellar
disc did not survive the merger event that created the KDC, }{\bf (How
  do you know there was a stellar disc to start with? Clarify or
  rephrase.)} \removed{it is unlikely that the gas in the progenitor of IC~1459
survived. However, the lost gas may have remained bound and been
re-accreted, so that the gas observed today preserves a fossil record
of the galaxy's original disc. Alternatively, the ISM may have yet
another external origin.}

@@

\removed{Generally, } If we assume that the different ionisation states of a
given atomic species\added{, observed along the same line-of-sight,} occur in 
the same spatial location \added{(and therefore are produced under the same 
conditions)}\removed{, then shielding by dust is not important or at worst its 
effect on the emission-line ratios is linear.} \textbf{(Why is the effect only 
linear? Justify.)} \removed{Given that the different states are then produced under
the same conditions,} it is natural to expect a simple relationship
between their emission line fluxes, similar to that of the Balmer
decrement between H$\alpha$ and H$\beta$. We exploit such
relationships here, to transform the classification boundaries of
commonly-used diagnostic plots that utilise emission lines outside of
the VIMOS spectral range, to diagnostics that can be measured with our
VIMOS data. In particular, we transform the classic BPT
[\ion{N}{ii}]/H$\alpha$ versus [\ion{O}{iii}]/H$\beta$ diagram to
[\ion{N}{i}]/H$\beta$ versus [\ion{O}{iii}]/H$\beta$ (hereafter the
SAURON diagnostic plot) following \citet{Sarzi2010}.

@@

The two transformations that we use are from the
[\ion{N}{ii}]/H$\alpha$ to the [\ion{N}{i}]/H$\beta$ line ratio and
from the H$\alpha$ to the H$\beta$ equivalent width (EW). In both
cases, we fit a linear relationship using the least-trimmed squares
routine
\textsc{lts\_linefit}\footnote{http://www-astro.physics.ox.ac.uk/\~mxc/software/\#lts}
of \citet{Cappellari2013}, because of its robust handling of the
uncertainties along both axes. The linear relationships are shown in
Figs.~\ref{fig:ratio_relation} and \ref{fig:EqW_relation}, where we
respectively find
\begin{equation}
  \frac{[\text{\ion{N}{ii}}]}{H\alpha}=(0.48\pm0.02)\,\frac{[\text{\ion{N}{i}}]}{H\beta}+(1.62\pm0.01)
\end{equation}
and	
\begin{equation}
  \mathrm{EW}(H\alpha)=(2.82\pm0.02)\,\mathrm{EW}(H\beta)+(0.13\pm0.02)~.
  \label{eq:EqW_dec}
\end{equation}
As [\ion{N}{ii}]/H$\alpha<1.80$ is occasionally observed and would
result in an unphysical negative [\ion{N}{i}]/H$\beta$ line ratio if
used blindly, we instead use the following transformation in practice:
\begin{equation}
  \frac{[\text{\ion{N}{ii}}]}{H\beta}= 
  \begin{cases}
    (0.48\pm0.02)\,\frac{[\text{\ion{N}{i}}]}{H\beta}+(1.62\pm0.01), & \text{if}~\frac{[\text{\ion{N}{i}}]}{H\alpha}>0.5 \\
    (3.72\pm0.03)\,\frac{[\text{\ion{N}{i}}]}{H\beta}, & \text{otherwise.}
  \end{cases}
  \label{eq:N_dec}
\end{equation}

{\bf (There is something very wrong about this last set of
  equations. First, since you presumably want to infer
  $\frac{[\text{\ion{N}{i}}]}{H\beta}$ from
  $\frac{[\text{\ion{N}{iI}}]}{H\alpha}$ and EW(H$\beta$) from
  EW(H$\alpha$), why not report (and presumably fit for in the first
  place) the inverse of the Eqs.~A1 and A2. Second, you have switched
  $\frac{[\text{\ion{N}{i}}]}{H\beta}$ and
  $\frac{[\text{\ion{N}{iI}}]}{H\alpha}$ in Eq.~A3, which is clearly
  wrong. You should probably switch them back. In addition, the
  conditions stated in Eq.~A3 make no sense. Presumably, one should
  follow the relation until $\frac{[\text{\ion{N}{i}}]}{H\beta}=0$,
  and then leave it at $0$. In any case, these equations need to be
  fixed.) JW: Fixed - note the method I am using for highlighting does not let me highlight within an equation environment so only the new version is shown.}
